Non-word repetition in Yélî Dnye

### 2020-12-18 manuscript.tex
minor typo fixes

Most words in Yélî Dnye are bisyllabic (\textasciitilde{}50\%), with
monosyllabic words (\textasciitilde{}40\%) appearing most commonly after
that, and with tri-and-above syllabic words appearing least frequently
(\textasciitilde{}10\%; based on \textgreater{}5800 lexemes in the most
recent Yélî Dnye dictionary at time of writing; Levinson, accepted). The
vast majority of syllables use a CV format. A small portion of the
lexicon features words with a final closed syllable, limited to codas of
-/m/, -/p/, or -/j/ (e.g., `ndap' (Spondylus shell) /ṇṭæp/). However, in
spontaneous speech an epenthetic /ɯ/ is often inserted after word-final
coda, yielding a CV.CV structure instead (e.g., `ndapî' /ṇṭæ.pɯ/). This
process is used frequently with English loan words that have a coda
(e.g., `ponî' (phone) /`pɔ.nɯ/). An even smaller portion of the lexicon
features words starting with a vowel (e.g., 'ala' (here) /æ.læ/), but
these are limited to /æ/-. Finally, the lexicon features a handful of
single-vowel grammatical morphemes (see Levinson (accepted) for
details).

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/prevlit-fig-1.pdf}
\caption{\label{fig:prevlit-fig}NWR scores as a function of age (in years)
and item length for comparable studies. Arabic data from Jaber et al.
(2018); Italian data from Piazzalunga et al. (2019); Tsimane' from
Cristia et al. (2020); Yélî data from the present study.}
\end{figure}

@@

A first list of candidate items was generated during a trip to the
island in 2018 by selecting simple consonants (/p/, /t/, /ṭ/, /k/, /m/,
/n/, /w/, /y/) and vowels (/i/, /o/, /u/, /a/, /e/) and combining them
into consonant-vowel syllables, then sampling the space of 1- to
4-syllable sequences. These candidates were automatically removed from
consideration if they appeared in Levinson's (2015) dictionary. The
second author presented them orally to three local research assistants,
all native speakers of Yélî Dnye, who were repeated each form, as they
would in an NWR task, and additinally let the experimenter know if the
item was in fact a word or phrase in Yélî Dnye. Any item reported to
have a meaning or a strong association with another word form or meaning
was excluded.

@@

A Praat script (Boersma \& Weenink, 2020) was written to randomize this
list 20 times, and split it into two sublists, to generate 40 different
elicitation sets. The 40 elicitation sets are available online from
\url{https://osf.io/5qspb}. The split had the following constraints:

\begin{itemize}
\tightlist
\item
  The same three items were selected as practice items and used in all
  40 elicitation sets
\item
  Splits were done within each length group from the 2018 items (i.e.,
  separately for 2-, 3-, and 4-syllable items); and among onset groups
  for the difficult monosyllables generated in 2019 (i.e., all the
  monosyllables starting with /tp/ were split into 2 sublists). Since
  some of these groups had an odd number of items, one of the sublists
  was slightly longer than the other (20 vs.~23).
\item
  Once the sublist split had been done, items were randomized such that
  all children heard first the 3 practice items in a fixed order (1-,
  2-, and 4-syllable), a randomized version of their sublist selection
  of difficult onset items, and randomized versions of their 2-syllable,
  then 3-syllable, and finally 4-syllable items.
\end{itemize}

>>>>

Most words in Yélî Dnye are bisyllabic (\textasciitilde{}50\%), with
monosyllabic words (\textasciitilde{}40\%) appearing most commonly after
that, and with tri-and-above syllabic words appearing least frequently
(\textasciitilde{}10\%; based on \textgreater{}5800 lexemes in the most
recent Yélî Dnye dictionary at time of writing; Levinson, accepted). The
vast majority of syllables use a CV format. A small portion of the
lexicon features words with a final closed syllable, limited to codas of
-/m/, -/p/, or -/j/ (e.g., `ndap' (Spondylus shell) /ṇṭæp/). However, in
spontaneous speech an epenthetic /ɯ/ is often inserted after word-final
coda, yielding a CV.CV structure instead (e.g., `ndapî' /`ṇṭæ.pɯ/). This
process is used frequently with English loan words that have a coda
(e.g., 'ponî' (phone) /`pɔ.nɯ/). An even smaller portion of the lexicon
features words starting with a vowel (e.g., 'ala' (here) /æ.'læ/), but
these are limited to /æ/-. Finally, the lexicon features a handful of
single-vowel grammatical morphemes (see Levinson (accepted) for
details).

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/prevlit-fig-1.pdf}
\caption{\label{fig:prevlit-fig}NWR scores as a function of age (in years)
and item length for comparable studies. Arabic data from Jaber et al.
(2018); Italian data from Piazzalunga et al. (2019); Tsimane' from
Cristia et al. (2020); Yélî Dnye data from the present study.}
\end{figure}

@@

A first list of candidate items was generated during a trip to the
island in 2018 by selecting simple consonants (/p/, /t/, /ṭ/, /k/, /m/,
/n/, /w/, /y/) and vowels (/i/, /o/, /u/, /a/, /e/) and combining them
into consonant-vowel syllables, then sampling the space of 1- to
4-syllable sequences. These candidates were automatically removed from
consideration if they appeared in Levinson's (2015) dictionary. The
second author presented them orally to three local research assistants,
all native speakers of Yélî Dnye, who repeated each form as they would
in an NWR task and additinally let the experimenter know if the item was
in fact a word or phrase in Yélî Dnye. Any item reported to have a
meaning or a strong association with another word form or meaning was
excluded.

@@

A Praat script (Boersma \& Weenink, 2020) was written to randomize this
list 20 times, and split it into two sublists, to generate 40 different
elicitation sets. The 40 elicitation sets are available online from
\href{https://osf.io/5qspb}{osf.io/5qspb}. The split had the following
constraints:

\begin{itemize}
\tightlist
\item
  The same three items were selected as practice items and used in all
  40 elicitation sets.
\item
  Splits were done within each length group from the 2018 items (i.e.,
  separately for 2-, 3-, and 4-syllable items); and among onset groups
  for the difficult monosyllables generated in 2019 (i.e., all the
  monosyllables starting with /tp/ were split into 2 sublists). Since
  some of these groups had an odd number of items, one of the sublists
  was slightly longer than the other (20 vs.~23).
\item
  Once the sublist split had been done, items were randomized such that
  all children heard first the 3 practice items in a fixed order (1-,
  2-, and 4-syllable), a randomized version of their sublist selection
  of difficult onset items, and randomized versions of their 2-syllable,
  then 3-syllable, and finally 4-syllable items.
\end{itemize}
